Agents and you, a brief summary

### 2015-11-01 agents/summery.tex
added soem info abut fixed points...

\subsection{Utility pump}
A utility pump is a MRP in which at least one recurrent state possesses a
non-zero reward.
\subsubsection{Discount factor}
A \emph{dicsount factor} is a real number $0 \le \gamma < 1$. it represents
the probability to survive from one state to the next.

@@

\[B_p : \mathbb{R}^n \to \mathbb{R}^n : v \mapsto C + \gamma Pv \]
\subsection{Exam}
 For a given decision problem with a certain
discount factor.A pure policy sufices.
Do policy iteration, (a single iteration), do value iteration
(single iteration).

>>>>

\subsubsection{Utility pump}
A utility pump is a MRP in which at least one recurrent state possesses a
non-zero reward.
\subsubsection{Discount factor}
A \emph{dicsount factor} is a real number $0 \le \gamma < 1$. it represents
the probability to survive from one state to the next.

@@

\[B_p : \mathbb{R}^n \to \mathbb{R}^n : v \mapsto C + \gamma Pv \]

\subsection{Fixed point}
The value vector, $v^*$, of a discounted reward Markov process is a fixed
point of the $B_p$ operator:

\[ B_p(v)=v\]

\[
	v_0 \to B_p(v_0) \to B_p B_p (v_0) \to \dots \to B^n_P v_0
	\to \dots \to v^*
\]

\subsection{Exam}
 For a given decision problem with a certain
discount factor.A pure policy sufices.
Do policy iteration, (a single iteration), do value iteration
(single iteration).
